Bayesian analysis of the NESTA study of interventions against verbal aggression online

### 2021-09-14 bayesianAnalysis/bayesianReport.Rmd
adding contrasts

@@

>>>>

removeX <-   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

removeY <-   theme(axis.title.y=element_blank(),
                   axis.text.y=element_blank(),
                   axis.ticks.y=element_blank())

@@

# Inspecting the model and effect sizes

We start by using the \textsf{Final} model formula to build a model, this time using Hamiltionian Monte Carlo. We leave the code commented out and load a pre-compiled model for computational convenience

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
# FinalHMC <- ulam(
#   alist(
#     AdiffS ~ dnorm( mu, sigma ),
#     mu <- a + bADS[groupID] * ADS +  bIT[groupID] +
#     bIC[groupID] * IC + bADSIC * ADS * IC+
#     bCBS[groupID] *CBS,
#     a ~ dnorm (0,0.3),
#     bADS[groupID] ~ dnorm(0,.3),
#     bADSIC ~ dnorm(0,.3),
#     bCBS[groupID] ~ dnorm(0,.3),
#     bIT[groupID] ~ dnorm(0,.3),
#     bIC[groupID] ~ dnorm(0,.3),
#     sigma  ~ dexp(1)
#   ),
#   data = summaries
# )
# saveRDS(FinalHMC, file = "models/FinalHMC.rds")

FinalHMC <- readRDS(file = "models/FinalHMC.rds")
```
\normalsize
First, let's take a look at the best model coefficients.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%"}
precis(FinalHMC, depth = 2)
plot(precis(FinalHMC, depth = 2))
```
\normalsize

These, however, are notoriously hard to interpret in models with interactions. For this reason, it is better to plot predicted effects for various combinations of predictors.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}

visGroup <- function (model, ADS, CBS, xmin =2, ymax = -3)
{
groupID <- 1:3
IC <- 5 
data <- expand.grid(ADS = ADS,groupID = groupID, CBS = CBS, IC =  IC)
posterior <- extract.samples(model, n = 1e5)
mu <- link( model, data=data ) 
colnames(mu) <- levels(summaries$group)
muLong <- melt(mu)
colnames(muLong) <- c("id", "group", "AdiffS")
means <-  round(apply(mu , 2 , mean ), 2)
mu_HPDI <- round(apply( mu , 2 , HPDI ),2)
means <- as.data.frame(means)
means$group <- rownames(means)
rownames(means) <- NULL
meansDisp <- cbind(means,t(as.data.frame(mu_HPDI)))
meansDisp <- meansDisp[,c(1,3,4)]

plot <- ggplot(muLong)+geom_violin(aes(x = group, y = AdiffS), alpha = 0.2)+
  xlab("")+
  labs(title = paste("ADS=", ADS, ", CBS=",  CBS,  sep = ""))+
  theme_tufte()+ylim(c(-4,4))
#+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)
return(plot)
}

visGroupA2C_2 <- visGroup(model = FinalHMC, ADS = 2,CBS = -2)
visGroupA2C0 <- visGroup(model = FinalHMC, ADS = 2,CBS = 0 )
visGroupA2C2 <- visGroup(model = FinalHMC, ADS = 2,CBS = 2)

visGroupA0C_2 <- visGroup(model = FinalHMC, ADS = 0,CBS = -2 )
visGroupA0C0 <- visGroup(model = FinalHMC, ADS = 0,CBS = 0 )
visGroupA0C2 <-  visGroup(model = FinalHMC, ADS = 0,CBS = 2)

visGroupA2C_2 <-  visGroup(model = FinalHMC, ADS = 2,CBS = -2 )
visGroupA2C0 <- visGroup(model = FinalHMC, ADS = 2,CBS = 0 )
visGroupA2C2 <- visGroup(model = FinalHMC, ADS = 2,CBS = 2 )

visGroupJoint <- ggarrange(visGroupA2C_2+removeX + ggtitle("CBS = -2")+ylab("ADS = 2") , visGroupA2C0+theme_void()+ ggtitle("CBS = 0"),visGroupA2C2+theme_void()+ ggtitle("CBS = 2"), 
          visGroupA0C_2+removeX+ylab("ADS = 0")+ggtitle(""), visGroupA0C0+theme_void()+ggtitle(""), visGroupA0C2+theme_void()+ggtitle(""),
          visGroupA2C_2+ylab("ADS = -2")+ggtitle(""), visGroupA2C0+removeY+ggtitle(""), visGroupA2C2+removeY+ggtitle(""), ncol =3, nrow = 3)

visGroupJoint2 <- annotate_figure(visGroupJoint, 
  top = text_grob("(range restricted to (-4,4), IC at the rounded mean = 5)",
                  size = 10))
visGroupJoint3 <- annotate_figure(visGroupJoint2, 
  top = text_grob("Predicted change in attacks by activity type and treatment groups (standardized)",
                  size = 12))

visGroupJoint3 
```
\normalsize

To gain more clarity, let's look at predicted contrasts, here understood as distances from the control group mean, by activity types, first versus CBS, then versus ADS.

\vspace{1mm}
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", message = FALSE, warning = FALSE}
visContrastsCBS <- function(model = FinalHMC, ADS = ADS , IC =  5,
                            CBS = seq(-3,3,by  = 0.1))
  {
  groupID <- 1:3
  data <- expand.grid(ADS, groupID, IC , CBS)
  colnames(data) <- c("ADS", "groupID", "IC", "CBS")
  posterior <- extract.samples(model, n = 1e5)
  link( model, data=data ) 
  mu <- link( model, data=data ) 
  means <-  round(apply(mu , 2 , mean ), 4)
  HPDIs <- round(apply( mu , 2 , HPDI ),4)
  visContrast <- cbind(data,means,t(as.data.frame(HPDIs)))

  ones <- 3 * (1:(nrow(visContrast)/3))-2
  twos <- 3 * (1:(nrow(visContrast)/3))-1
  threes <- 3 * (1:(nrow(visContrast)/3))

  colnames(visContrast)[c(6,7)] <- c("low", "high")
  contrast <- numeric(nrow(visContrast))
  cLow <- numeric(nrow(visContrast))
  cHigh <- numeric(nrow(visContrast))
  for(i in threes){
  contrast[i] <- visContrast$means[i] - visContrast$means[i-2]  
  }
  for(i in twos){
  contrast[i] <- visContrast$means[i] - visContrast$means[i-1]  
  }
  visContrast$contrast <- contrast
  visContrast$shift <-  visContrast$contrast - visContrast$means
  for(i in ones){
  visContrast$shift[i] <- 0
  }
  visContrast$cLow <- visContrast$low + visContrast$shift
  visContrast$cHigh <- visContrast$high + visContrast$shift

  visContrast$group = rep(c("control", "empathy", "normative"), 
                          nrow(visContrast)/3)

  visContrastTreatment <- visContrast[groupID !=1,]

  return(ggplot(visContrastTreatment, aes(x = CBS, y = contrast, color = group ))+
            geom_pointrange(mapping = 
        aes(ymin = cLow, ymax = cHigh), size = .2, alpha = .5) +theme_tufte())
}

visContrastCBSJoint <- ggarrange(visContrastsCBS(FinalHMC,ADS = -2)+
      ggtitle("ADS=-2")+ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
          visContrastsCBS(FinalHMC,ADS = 0)+ggtitle("ADS=0")+
        ylim(c(-2.5,2.5))+ scale_color_discrete(guide=FALSE),
        visContrastsCBS(FinalHMC,ADS = 2)+ggtitle("ADS=2")+
        ylim(c(-2.5,2.5))+ theme(legend.position = c(0.75, 0.1)), ncol = 3)

visContrastCBSJoint2 <- annotate_figure(visContrastCBSJoint, 
      top = text_grob("(range restricted to (-2.5,2.5), IC at the rounded mean = 5)",
                                size = 10))
visContrastCBSJoint3 <- annotate_figure(visContrastCBSJoint2, 
top = text_grob("Predicted distance from the control group mean vs. CBS  (standardized)",
                                size = 12))

visContrastCBSJoint3
```
\normalsize

### 2021-09-14 bayesianAnalysis/bayesianReport.tex
adding contrasts

\NormalTok{plot <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \KeywordTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS, }\StringTok{", IC=5"}\NormalTok{, }\DataTypeTok{sep =} \StringTok{""}\NormalTok{))}\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{(}\DataTypeTok{base_size =} \DecValTok{6}\NormalTok{)}
\CommentTok{#+ }
\CommentTok{#  annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
\KeywordTok{return}\NormalTok{(plot)}
\NormalTok{\}}

\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \FloatTok{-3.5}\NormalTok{ )}

\NormalTok{visGroupA0C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
\NormalTok{visGroupA0C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
\NormalTok{visGroupA0C2 <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-4}\NormalTok{ )}

\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ , }\DataTypeTok{ymax =} \DecValTok{-2}\NormalTok{)}
\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{, }\DataTypeTok{ymax =} \DecValTok{-4}\NormalTok{ )}

\NormalTok{visGroupJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(visGroupA2C_}\DecValTok{2}\NormalTok{ , visGroupA2C0,visGroupA2C2, }
\NormalTok{          visGroupA0C_}\DecValTok{2}\NormalTok{, visGroupA0C0, visGroupA0C2,}
\NormalTok{          visGroupA2C_}\DecValTok{2}\NormalTok{, visGroupA2C0, visGroupA2C2, }\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}\NormalTok{)}

\NormalTok{visGroupJoint}
\end{Highlighting}
\end{Shaded}

@@

>>>>

\NormalTok{plot <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{(muLong)}\OperatorTok{+}\KeywordTok{geom_violin}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ group, }\DataTypeTok{y =}\NormalTok{ AdiffS), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{""}\NormalTok{)}\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{title =} \KeywordTok{paste}\NormalTok{(}\StringTok{"ADS="}\NormalTok{, ADS, }\StringTok{", CBS="}\NormalTok{,  CBS,  }\DataTypeTok{sep =} \StringTok{""}\NormalTok{))}\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_tufte}\NormalTok{()}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\DecValTok{4}\NormalTok{,}\DecValTok{4}\NormalTok{))}
\CommentTok{#+   annotation_custom(tableGrob(meansDisp), xmin=xmin,  ymax=ymax)}
\KeywordTok{return}\NormalTok{(plot)}
\NormalTok{\}}

\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{)}
\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}

\NormalTok{visGroupA0C_}\DecValTok{2}\NormalTok{ <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ )}
\NormalTok{visGroupA0C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
\NormalTok{visGroupA0C2 <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{)}

\NormalTok{visGroupA2C_}\DecValTok{2}\NormalTok{ <-}\StringTok{  }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{-2}\NormalTok{ )}
\NormalTok{visGroupA2C0 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{0}\NormalTok{ )}
\NormalTok{visGroupA2C2 <-}\StringTok{ }\KeywordTok{visGroup}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{,}\DataTypeTok{CBS =} \DecValTok{2}\NormalTok{ )}

\NormalTok{visGroupJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(visGroupA2C_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX }\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 2"}\NormalTok{) , visGroupA2C0}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 0"}\NormalTok{),visGroupA2C2}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\StringTok{ }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"CBS = 2"}\NormalTok{), }
\NormalTok{          visGroupA0C_}\DecValTok{2}\OperatorTok{+}\NormalTok{removeX}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = 0"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C0}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA0C2}\OperatorTok{+}\KeywordTok{theme_void}\NormalTok{()}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{),}
\NormalTok{          visGroupA2C_}\DecValTok{2}\OperatorTok{+}\KeywordTok{ylab}\NormalTok{(}\StringTok{"ADS = -2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C0}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), visGroupA2C2}\OperatorTok{+}\NormalTok{removeY}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{""}\NormalTok{), }\DataTypeTok{ncol =}\DecValTok{3}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{3}\NormalTok{)}

\NormalTok{visGroupJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupJoint, }
  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-4,4), IC at the rounded mean = 5)"}\NormalTok{,}
                  \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
\NormalTok{visGroupJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visGroupJoint2, }
  \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted change in attacks by activity type and treatment groups (standardized)"}\NormalTok{,}
                  \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}

\NormalTok{visGroupJoint3 }
\end{Highlighting}
\end{Shaded}

@@

To gain more clarity, let's look at predicted contrasts, here understood
as distances from the control group mean, by activity types, first
versus CBS, then versus ADS.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{visContrastsCBS <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ FinalHMC, }\DataTypeTok{ADS =}\NormalTok{ ADS , }\DataTypeTok{IC =}  \DecValTok{5}\NormalTok{,}
                            \DataTypeTok{CBS =} \KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{3}\NormalTok{,}\DecValTok{3}\NormalTok{,}\DataTypeTok{by  =} \FloatTok{0.1}\NormalTok{))}
\NormalTok{  \{}
\NormalTok{  groupID <-}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{3}
\NormalTok{  data <-}\StringTok{ }\KeywordTok{expand.grid}\NormalTok{(ADS, groupID, IC , CBS)}
  \KeywordTok{colnames}\NormalTok{(data) <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"ADS"}\NormalTok{, }\StringTok{"groupID"}\NormalTok{, }\StringTok{"IC"}\NormalTok{, }\StringTok{"CBS"}\NormalTok{)}
\NormalTok{  posterior <-}\StringTok{ }\KeywordTok{extract.samples}\NormalTok{(model, }\DataTypeTok{n =} \FloatTok{1e5}\NormalTok{)}
  \KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
\NormalTok{  mu <-}\StringTok{ }\KeywordTok{link}\NormalTok{( model, }\DataTypeTok{data=}\NormalTok{data ) }
\NormalTok{  means <-}\StringTok{  }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(mu , }\DecValTok{2}\NormalTok{ , mean ), }\DecValTok{4}\NormalTok{)}
\NormalTok{  HPDIs <-}\StringTok{ }\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{( mu , }\DecValTok{2}\NormalTok{ , HPDI ),}\DecValTok{4}\NormalTok{)}
\NormalTok{  visContrast <-}\StringTok{ }\KeywordTok{cbind}\NormalTok{(data,means,}\KeywordTok{t}\NormalTok{(}\KeywordTok{as.data.frame}\NormalTok{(HPDIs)))}

\NormalTok{  ones <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{2}
\NormalTok{  twos <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}\OperatorTok{-}\DecValTok{1}
\NormalTok{  threes <-}\StringTok{ }\DecValTok{3} \OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{))}

  \KeywordTok{colnames}\NormalTok{(visContrast)[}\KeywordTok{c}\NormalTok{(}\DecValTok{6}\NormalTok{,}\DecValTok{7}\NormalTok{)] <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"low"}\NormalTok{, }\StringTok{"high"}\NormalTok{)}
\NormalTok{  contrast <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
\NormalTok{  cLow <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
\NormalTok{  cHigh <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\KeywordTok{nrow}\NormalTok{(visContrast))}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ threes)\{}
\NormalTok{  contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-2}\NormalTok{]  }
\NormalTok{  \}}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ twos)\{}
\NormalTok{  contrast[i] <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i] }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means[i}\DecValTok{-1}\NormalTok{]  }
\NormalTok{  \}}
\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{contrast <-}\StringTok{ }\NormalTok{contrast}
\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift <-}\StringTok{  }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{contrast }\OperatorTok{-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{means}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ones)\{}
\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{shift[i] <-}\StringTok{ }\DecValTok{0}
\NormalTok{  \}}
\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cLow <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{low }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}
\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{cHigh <-}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{high }\OperatorTok{+}\StringTok{ }\NormalTok{visContrast}\OperatorTok{$}\NormalTok{shift}

\NormalTok{  visContrast}\OperatorTok{$}\NormalTok{group =}\StringTok{ }\KeywordTok{rep}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"control"}\NormalTok{, }\StringTok{"empathy"}\NormalTok{, }\StringTok{"normative"}\NormalTok{), }
                          \KeywordTok{nrow}\NormalTok{(visContrast)}\OperatorTok{/}\DecValTok{3}\NormalTok{)}

\NormalTok{  visContrastTreatment <-}\StringTok{ }\NormalTok{visContrast[groupID }\OperatorTok{!=}\DecValTok{1}\NormalTok{,]}

  \KeywordTok{return}\NormalTok{(}\KeywordTok{ggplot}\NormalTok{(visContrastTreatment, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ CBS, }\DataTypeTok{y =}\NormalTok{ contrast, }\DataTypeTok{color =}\NormalTok{ group ))}\OperatorTok{+}
\StringTok{            }\KeywordTok{geom_pointrange}\NormalTok{(}\DataTypeTok{mapping =} 
        \KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymin =}\NormalTok{ cLow, }\DataTypeTok{ymax =}\NormalTok{ cHigh), }\DataTypeTok{size =} \FloatTok{.2}\NormalTok{, }\DataTypeTok{alpha =} \FloatTok{.5}\NormalTok{) }\OperatorTok{+}\KeywordTok{theme_tufte}\NormalTok{())}
\NormalTok{\}}

\NormalTok{visContrastCBSJoint <-}\StringTok{ }\KeywordTok{ggarrange}\NormalTok{(}\KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{-2}\NormalTok{)}\OperatorTok{+}
\StringTok{      }\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=-2"}\NormalTok{)}\OperatorTok{+}\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
          \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{0}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=0"}\NormalTok{)}\OperatorTok{+}
\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_discrete}\NormalTok{(}\DataTypeTok{guide=}\OtherTok{FALSE}\NormalTok{),}
        \KeywordTok{visContrastsCBS}\NormalTok{(FinalHMC,}\DataTypeTok{ADS =} \DecValTok{2}\NormalTok{)}\OperatorTok{+}\KeywordTok{ggtitle}\NormalTok{(}\StringTok{"ADS=2"}\NormalTok{)}\OperatorTok{+}
\StringTok{        }\KeywordTok{ylim}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\OperatorTok{-}\FloatTok{2.5}\NormalTok{,}\FloatTok{2.5}\NormalTok{))}\OperatorTok{+}\StringTok{ }\KeywordTok{theme}\NormalTok{(}\DataTypeTok{legend.position =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.75}\NormalTok{, }\FloatTok{0.1}\NormalTok{)), }\DataTypeTok{ncol =} \DecValTok{3}\NormalTok{)}

\NormalTok{visContrastCBSJoint2 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastCBSJoint, }
      \DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"(range restricted to (-2.5,2.5), IC at the rounded mean = 5)"}\NormalTok{,}
                                \DataTypeTok{size =} \DecValTok{10}\NormalTok{))}
\NormalTok{visContrastCBSJoint3 <-}\StringTok{ }\KeywordTok{annotate_figure}\NormalTok{(visContrastCBSJoint2, }
\DataTypeTok{top =} \KeywordTok{text_grob}\NormalTok{(}\StringTok{"Predicted distance from the control group mean vs. CBS  (standardized)"}\NormalTok{,}
                                \DataTypeTok{size =} \DecValTok{12}\NormalTok{))}

\NormalTok{visContrastCBSJoint3}
\end{Highlighting}
\end{Shaded}

\begin{center}\includegraphics[width=1\linewidth]{bayesianReport_files/figure-latex/unnamed-chunk-15-1} \end{center}
